Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-16 constantRate/ConstCompFuzzExt.tex
reorganized with block guessable first

Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.  Then $\Hav(C | C_{\mathcal{I}^c}) \geq |C| - \beta$.  We now show that codewords that differ only positions of $\mathcal{I}$ are indistinguishable.
\begin{lemma}
\label{lem:codewords in I close}
Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then, 
\[
\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < 2^{\alpha+1}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq \alpha$.  The only information about $C_i$ is contained in the query responses.  Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with probability $1-2^{-\alpha+1}$ all responses to $c_i$ are $0$.  Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $>2^{-\alpha+1}$.  Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is at most $q/2^n$.  Thus, it must occur with probability:
\begin{align*}
2^{-\alpha+1}&>\Pr[\text{non zero response location }i]\\
\Pr[\text{non zero response location }i] &= \Pr[c_i =1]\Pr[\text{non zero response location }i\wedge c_i=1] \\&+ \Pr[c_i=0] \Pr[\text{non zero response location }i \wedge c_i=0]\\
&=1/2 \times 2^{-n+\log q} + 1/2 \Pr[\text{non zero response location }i \wedge c_i=0]
\end{align*}
We now show that $n-\log q \geq \alpha$:
\begin{claim}
$n-\log q \geq \alpha$
\end{claim}
\begin{proof}
Consider one particular $i \in \mathcal{I}$.  It suffices to show that there exists an adversary $A$ making $q$ queries such that the remaining entropy in that block is at most $n-\log (q+1)$.  Let $W_i$ be a distribution, consider $A$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.  After these queries, Then, the remaining min-entropy is at most:
\begin{align*}
\Hav(W_i | View(A)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
&=-\log\left( 2^{-n+\log q} \right) = n-\log q
\end{align*}
\end{proof}

@@

\begin{lemma}
\label{lem:blocks unguessable after queries}
Let $n$ be a security parameter.  Let $W(n) = W = W_1,..., W_\ell$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = k = \omega(\log n)$.  Then let $\mathcal{A}$ be an adversary making a polynomial, $q = \poly(n)$, number of oracle equality queries for blocks $i$.  %Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}. 
Then $\forall i, \Hav(W_i | View(A))  = k- \log (q+1)$.  Furthermore, since $W_i$ are independent $\Hav(W | View(A))= \ell (k-\log (q+1))$.
\end{lemma}
\begin{proof}
Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.  We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).  The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.  (All the dependence between $W_i$ and the queries is contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.  There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.  If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.  These responses can be removed as the response is deterministic.  Let $A'$ represent the sequence with all duplicate queries removed.  This sequence has at most a single $1$.  Thus, the total number of possible responses is $q+1$.  Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
&=\Hav(W_i |A') \\
&=\Hoo(W_i) - \log |A'|\\
&=k - \log |A'|\\
&=k - \log (q+1)
\end{align*}
Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
This argument holds for all $i$.  This completes the proof.
\end{proof}

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,..., W_\ell$ be a source where blocks are independent.  Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.  Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
\end{claim}
\begin{proof}
We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.  It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.  As argued in the proof of \lemref{lem:blocks unguessable after queries}, we can consider the sequence of queries without duplicates~(as duplicate queries provide no additional information and do not increase the number of possible response strings).  Then there are at most $q+1$ possible response strings~(all strings of Hamming weight at most $1$).  Then by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have that 
\[
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hav(W_i | View(A^{\mathcal{O}_{W}(i, \cdot)})) \geq \Hoo(W_i) -\log (q+1).
\]
\end{proof}
In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  This is a subset of the distributions in \clref{cl:independent high ent}.

@@

\section{Discussion}
\label{sec:discussion}
Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.  Correction occurs for a small number of dimensions that are allowed to vary completely.  As described in \secref{sec:supported sources}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).

>>>>

Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.  Then $\Hav(C | C_{\mathcal{I}^c}) \geq |C| - \beta$~(by \clref{cl:many locations ent}).  We now show that codewords differing in positions of $\mathcal{I}$ are indistinguishable.
\begin{lemma}
\label{lem:codewords in I close}
Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then, 
\[
\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < 2^{\alpha+1}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq \alpha$.  The only information about $C_i$ is contained in the query responses.  Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with probability $1-2^{-\alpha+1}$ all responses to $c_i$ are $0$.  Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $>2^{-\alpha+1}$.  Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is at most $q/2^n$.  Thus, it must occur with probability:
\begin{align*}
2^{-\alpha+1}&>\Pr[\text{non zero response location }i]\\
\Pr[\text{non zero response location }i] &= \Pr[c_i =1]\Pr[\text{non zero response location }i\wedge c_i=1] \\&+ \Pr[c_i=0] \Pr[\text{non zero response location }i \wedge c_i=0]\\
&=1/2 \times 2^{-n+\log q} + 1/2 \Pr[\text{non zero response location }i \wedge c_i=0]
\end{align*}
We now show that $n-\log q \geq \alpha$:
\begin{claim}
$n-\log q \geq \alpha$
\end{claim}
\begin{proof}
Consider one particular $i \in \mathcal{I}$.  It suffices to show that there exists an adversary $A$ making $q$ queries such that the remaining entropy in that block is at most $n-\log (q+1)$.  Let $W_i$ be a distribution, consider $A$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.  After these queries, Then, the remaining min-entropy is at most:
\begin{align*}
\Hav(W_i | View(A)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
&=-\log\left( 2^{-n+\log q} \right) = n-\log q
\end{align*}
\end{proof}

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,..., W_\ell$ be a source where blocks are independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.  Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
\end{claim}
\begin{proof}
We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.  It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.  
Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.  We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).  The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.  There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.  If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.  These responses can be removed as the response is deterministic.  Let $A'$ represent the sequence with all duplicate queries removed.  This sequence has at most a single $1$.  Thus, the total number of possible responses is $q+1$~(including the duplicates does not change the number of possible responses).  Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
&=\Hav(W_i |A') \\
&=\Hoo(W_i) - \log |A'|\\
&=\alpha - \log |A'|\\
&=\alpha - \log (q+1)
\end{align*}
Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
This argument holds for all $i$.  This completes the proof.
\end{proof}
In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  This is a subset of the distributions in \clref{cl:independent high ent}.

@@

\section{Discussion}
\label{sec:discussion}
Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.  Correction occurs for a small number of dimensions that are allowed to vary completely.  As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).
